\LARGE Untangling the link between traits, size and growth rate in plants

### 2016-07-28 ms/ms.tex
Standardise reference style to same as other papers

Functional traits capture core differences in the strategies
plants use to generate and invest surplus energy
 \citep{wright-2004, chave-2009, westoby-2002}.
Although most plants have the same basic physiological function
and key resource requirements (carbon, nitrogen and water), species differ considerably in
rates at which resources are acquired and invested into different tissues.
Much of this functional variation relates to underlying
differences in some prominent traits, including leaf
mass per area (LMA), wood density (WD), leaf nitrogen per area, vessel
diameter,  maximum  height (HMAX) and seed size  \citep{wright-2004,chave-2009}.
Data for these traits now exists for up to 10\% of the world's 250000 plant species
\citep{cornwell-2014}. Increasingly, researchers have been looking to traits
as potential indicators of the growth strategy and ecology of a species.

While the influence of plant traits on elements of plant physiological
function is increasingly understood, attempts at using traits to understand
demographic rates have met with mixed success
 \citep{wright-2010, poorter-2008}. In seedlings, the trait LMA
-- the central element of the leaf economics spectrum
 \citep{wright-2004} -- has been tightly related to relative growth
rate in plant mass \citep{lambers-1992, wright_cross-2000}. LMA and
its correlate leaf lifespan have also been linked to height growth rate for
small seedlings and saplings \citep{reich-1992, poorter-2006}. These
early successes prompted researchers to search for similar relationships in
large plants. However, the results showed that in trees LMA was not correlated
with diameter growth rate  \citep{wright-2010, poorter-2008,
herault-2011}. Meanwhile, other traits such as wood density showed
strong relationships to growth in large plants \citep{wright-2010},
but only weak relationships in seedlings  \citep{castro-diez-1998}. Thus
far, most trait growth relationships have been quantified for one or few
traits and at a single life- stage. Yet the picture is emerging is that the
link between traits and growth may be modified by plant size
 \citep{ruger-2012}. This finding challenges a wide-spread
assumption regarding traits: that particular ends of the trait spectrum translate directly into
faster or slower growth (refs XX).

The challenge of interpreting diverse empirical results seeking to link
traits to growth rate is made all the harder because we currently lack clear
expectations on the expected signal. Generating such expectations is one of the
primary role for theory \citep{kokko-2007}. Current empirical
results suggest the effect of traits on growth changes with size and possibly
also light environment, yet current theory says little about how such
relationships might come about. A widely-used model shows that for seedlings,
mass-based relative growth rate is linearly and negatively related to LMA
 \citep{lambers-1992, cornelissen-1996, wright_cross-2000}.
 An extension of the model suggests a similar
relationship may hold at larger sizes \citep{enquist-2007}. But as
described above, this prediction is not supported by empirical results.
Meanwhile, theoretical predictions on how other traits should influence growth
are largely absent.

A further problem with existing theory is that the effects of traits are all
realised via influences on mass production \citep{enquist-2007},
whereas the effect of traits such as LMA, WD, and Hmax is via allocated
to different tissues \citep{falster-2011}. There are in fact two problems with theory
focussed solely on mass production. The first is that measuring mass
production is only practical for small plants that can be easily harvested.
For larger plants, growth is more often measured as increment in either diameter
or height. For example, the CTFS monitors diameter growth in 49 large permanent
plots across forests worldwide \citep{anderson-teixeira-2015};
 forestry have likewise recorded growth in diameter across
large tracts of the globe \citep{purves-2008}. The second problem is
that, as we outline further below, because mass production is only one
component of plant growth; theory focussing solely on mass production will
 always be limited.

@@

Ultimately, trait based understanding integrated wiht model of plant growth, also able to cpature patterns of growth through ontogeny. Growth rates tend to show hump-shaped relationship with size, when expressed as either height \citep{sillett-2010, king-2011} or diameter growth \citep{herault-2011}.  In contrast, basal-area growth continues to increase with size \citep{sillett-2010, stephenson-2014}, due to an increasing influence of stem turnover. All growth measures decrease sharply with size when expressed as relative growth rates \citep{rees-2010, iida-2014}. Shade tolerance tends to decrease with increasing size \citep{lusk-2006}, due to increasing costs of mainatining stems \citep{givnish-1988}

In this paper we provide a mechanistic framework for describing the potential
effect of traits on growth throughout a plant's life-cycle, linking to
commonly used metrics such as height and diameter growth. To help motivate our
study we re-analyse demographic and trait data from an earlier study
 \citep{wright-2010}, to show 1) that the link between traits and
growth is stronger than previously thought, 2) that the influence of three
prominent traits on growth rate is moderated by plant size, and 3) that the
impact of size on the nature of relationships varies among traits
 \citep[see also]{ruger-2012}. We then show how these results align with new
set of theoretical predictions. Analysis extends ...
Moreover, we show how traits moderate plant
responses to light environment and also determine shade tolerance, supporting
diverse empirical results \citep{ruger-2012, poorter-2006}. By
disentangling the effects of plant size, light environment and traits on
growth rates, we hope to provide a solid theoretical foundation for trait
ecology and thus provide a platform for understanding growth across diverse
species around the world.

@@

To make sense of empirical patterns, we extend a widely-used theoretical model that links growth rate in
seedlings to LMA \citep{lambers-1992, wright_cross-2000}, to explicitly include influences of
size, light environment, and other prominent traits. This model

@@

We begin with a standard model for the amount of biomass available for
growth, ${\rm d}B / {\rm d}t$, given by the difference between income
(total photosynthesis) and losses (respiration and turnover) within the
plant \citep{makela-1997, Thornley-2000, falster-2011}:

@@

To model growth in either height, basal area or stem diameter requires that account not just for mass production, but also for the costs of building new tissues, allocation to reproduction, and architectural layout. Mathematically, height growth can be decomposed into a product of physiologically relevant terms \citep{falster-2011}:

@@

The first term on the right of eq \ref{eq:dhdt},
${\rm d}H / {\rm d}A_{\rm l}$, is the growth in plant height
per unit growth in total leaf area -- accounting for the architectural
strategy of the plant. Some species tend to leaf out more than grow
tall, while other species emphasise vertical
extension \citep{poorter-2006}.

@@

To address the first of these challenges, we use a functional balance
model \citep{yokozawa-1995,falster-2011} assuming
1) an allometric relation between total leaf area and plant height, and
2) a constant ratio between total leaf area and each of sapwood
cross-sectional area, bark cross-sectional area, and total root mass.
These assumptions, which are well-supported by data (Fig.
\ref{f-assumptions}), lead immediately to an allometric model for plant
size (Table \ref{tab:allometry}, see Supplementary material for
derivations). Substituting from Table \ref{tab:allometry} into eqs.
\ref{eq:dhdt}, \ref{eq:dast}, \ref{eq:dDdt} then gives an explicit model
for plant growth in relation to size.

@@

By definition, the main effect of increasing $\phi$ is to decrease the
marginal leaf deployment per mass (eq. \ref{eq:daldmt}) and thus reduce
growth rate. However, to fully account for the influence of $\phi$ on
growth we must also account for the decrease in leaf turnover that
results from superior leaf construction \citep{wright-2004}.
This is achieved by linking the turnover rate of leaf in eq.
\ref{eq:dbdt} to $\phi$. We use an allometric scaling relationship of
the form $k_{\rm l}=\alpha_4 \, \phi^{-\beta_4}$, which has been
shown to describe patterns across diverse
ecosystems \citep{wright-2004} (Fig. \ref{fS-leaf}).

As for leaf, cheaper stem construction (lower $\rho$) decreases the
cost of deploying a unit of leaf area, and may thereby increase growth
rates. However, the cost of cheap stem construction must also be
accounted for. However, the direct physiological trade-offs of lower
$\rho$ are less understood than for $\phi$. One possibility is that
lower $\rho$ decreases mechanical strength resulting in higher
mortality \citep{chave-2009, wright-2010}. Under
this scenario, decreasing $\rho$ will always provide a growth
advantage, because the costs of low $\rho$ are not realised within the
terms of eqs. \ref{eq:dhdt} and \ref{eq:dast} (Table
\ref{tab:trade-offs}). In addition, lower $\rho$ may increase turnover
of sapwood. Mirroring our assumptions for leaves, we let sapwood
turnover decrease with $\rho$,
i.e.$k_\textrm{ss}=\alpha_5 \, \rho^{-\beta_5}$, with $\beta_5 > 1$.

@@

This new growth model captures the intrinsically size-dependent nature
of plant growth, recovering well-known
empirical patterns \citep{sillett-2010, king-2011}. Height growth shows a hump-shaped pattern
with size, first increasing then decreasing. This pattern results from
systematic changes in the four components of eq. \ref{eq:dhdt} with size
(Fig. \ref{f-conceptual}), including a strong decline in the fraction of plant
that is leaf declines with increasing size (Fig. \ref{f-mass_fraction}),
and increasing reproductive allocation. In contrast, basal-area growth
continues to increase with size \citep{sillett-2010, stephenson-2014},
due to an increasing influence of stem
turnover. Diameter growth shows a weakly hump shaped
curve \citep{herault-2011}, tapering off slightly at larger
sizes, in part because of allometric effects (eq. \ref{eq:dDdt}, but
mainly because of increased reproductive allocation in older trees
(Fig?). All growth measures decrease sharply with size when expressed as
relative growth rates \citep{iida-2014}.

@@

Two other important predictions arise directly from linking traits to
growth rate. First, traits moderate the
responsiveness of growth to changes in light environment. This response
arises simply because species with higher potential growth rate have
greater potential plasticity. Recent analyses have shown that species
with low $rho$ increase growth more substantially with incraeses in
light \citep{ruger-2012}. This is exactly the behaviour
exhibited in our model (Fig. \ref{f-growth_light_dia}), at least for small
to intermediate sizes. At larger sizes (D=0.2m) however, the advantages
of low $\phi$ are lost (Fig. \ref{f-growth_light_dia}). This results also
agrees with empirical results showing that growth for species with low
$rho$ actually decreases as size
increases \citep{ruger-2012}. In contrast, growth rate tends
to increase in size for the species with highest
$\rho$ \citep{ruger-2012}.

Variation in $\phi$ also moderates the response of growth to changes
in light, with species having the lowest $rho$ being most responsive.
However, unlike for $\rho$, the effect appears only for the smallest
size classes. Accordingly, empirical analyses have detected such a link
in small plants but not for plants \textgreater{} 0.01m
dbh \citep{ruger-2012}.

@@

Current theory emphasises the relationship between $\phi$ and the relative growth in plant mass
\citep{lambers-1992, cornelissen-1996, wright_cross-2000,  enquist-2007},
${\rm d}P / {\rm d}t / M_{\rm a}$. This relationship can be derived from eq. \ref{eq:dbdt}  by ...
(see Appendix \ref{app:traits-RGR}).

@@

@Osazuwa-Peters-2014 - indreases in WD through ontogeny.

@@

Second, species with low $\phi$ and low $\rho$ are predicted to be
less shade tolerant (Fig. \ref{f-wplcp}). At low $\phi$ ($\rho$),
leaf (sapwood) turnover is higher and thus a greater light income is
needed to offset these costs. As previously suggested
 \citep{givnish-1988}, shade-tolerance also decreases with
height because as size increase, the total amount of energy needed to
offset respiratory and turnover costs in the stem also increases. These
finding matches well known empirical patterns, where both $\phi$ and
$\rho$ have been linked to shade tolerance \citep{poorter-2006, lusk-2008,osunkoya-1996}.

@@

Although Eq. \ref{eq:RGR} captures patterns of growth in seedlings in
relation to $\phi$\citep{wright_cross-2000}, this
approximation does not directly link to other traits, or to the
variables that are routinely collected for large trees: namely plant
height ($h$) and stem cross-sectional area ($A_{\rm st}$) or
diameter $D$.

@@

Note, scaling relationship reversed from \citep{falster-2011}.

@@

We follow the model of \citep{yokozawa-1995} describing the
vertical distribution of leaf area within the crowns of individual
plants. This model can account for a variety of canopy profiles through
a single parameter $\eta$. Setting $\eta=1$ results in a conical
canopy, as seen in many conifers, while higher values, e.g. $\eta=12$
, give a top-weighted canopy profile similar to those seen among
angiosperms. Let $S(z,h)$ be the sapwood area at height $z$ for a
plant with top height $h$. Following Yokozawa and Hara (1995) we
assume a relationship between $S(z,h)$ and height such that

@@

We also assume that each unit of sapwood area supports a fixed area of
leaf (the pipe model, \citep{shinozaki-1964}), so that the total
canopy area of a plant relates to basal sapwood area $S(0,h)$:

@@

where
$\eta_c=1-\frac{2}{1+\eta} + \frac{1}{1+2\eta}$ \citep{yokozawa-1995}.
Substituting from eq. \ref{eq:crown2} into eq. \ref{eq:ms1} gives an
expression for sapwood mass as a function leaf area and height:

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/lmA_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-construction cost.}
Data from \citep{wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship.\label{fS-leaf}}
\end{figure}

>>>>

Functional traits capture core differences in the strategies
plants use to generate and invest surplus energy
 \citep{Wright-2004, Chave-2009, Westoby-2002}.
Although most plants have the same basic physiological function
and key resource requirements (carbon, nitrogen and water), species differ considerably in
rates at which resources are acquired and invested into different tissues.
Much of this functional variation relates to underlying
differences in some prominent traits, including leaf
mass per area (LMA), wood density (WD), leaf nitrogen per area, vessel
diameter,  maximum  height (HMAX) and seed size  \citep{Wright-2004, Chave-2009}.
Data for these traits now exists for up to 10\% of the world's 250000 plant species
\citep{Cornwell-2014}. Increasingly, researchers have been looking to traits
as potential indicators of the growth strategy and ecology of a species.

While the influence of plant traits on elements of plant physiological
function is increasingly understood, attempts at using traits to understand
demographic rates have met with mixed success
 \citep{Wright-2010, Poorter-2008}. In seedlings, the trait LMA
-- the central element of the leaf economics spectrum
 \citep{Wright-2004} -- has been tightly related to relative growth
rate in plant mass \citep{Lambers-1992, Wright-2000}. LMA and
its correlate leaf lifespan have also been linked to height growth rate for
small seedlings and saplings \citep{Reich-1992, Poorter-2006}. These
early successes prompted researchers to search for similar relationships in
large plants. However, the results showed that in trees LMA was not correlated
with diameter growth rate  \citep{Wright-2010, Poorter-2008,
Herault-2011}. Meanwhile, other traits such as wood density showed
strong relationships to growth in large plants \citep{Wright-2010},
but only weak relationships in seedlings  \citep{Castro-1998}. Thus
far, most trait growth relationships have been quantified for one or few
traits and at a single life- stage. Yet the picture is emerging is that the
link between traits and growth may be modified by plant size
 \citep{Ruger-2012}. This finding challenges a wide-spread
assumption regarding traits: that particular ends of the trait spectrum translate directly into
faster or slower growth (refs XX).

The challenge of interpreting diverse empirical results seeking to link
traits to growth rate is made all the harder because we currently lack clear
expectations on the expected signal. Generating such expectations is one of the
primary role for theory \citep{Kokko-2007}. Current empirical
results suggest the effect of traits on growth changes with size and possibly
also light environment, yet current theory says little about how such
relationships might come about. A widely-used model shows that for seedlings,
mass-based relative growth rate is linearly and negatively related to LMA
 \citep{Lambers-1992, Cornelissen-1996, Wright-2000}.
 An extension of the model suggests a similar
relationship may hold at larger sizes \citep{Enquist-2007}. But as
described above, this prediction is not supported by empirical results.
Meanwhile, theoretical predictions on how other traits should influence growth
are largely absent.

A further problem with existing theory is that the effects of traits are all
realised via influences on mass production \citep{Enquist-2007},
whereas the effect of traits such as LMA, WD, and Hmax is via allocated
to different tissues \citep{Falster-2011}. There are in fact two problems with theory
focussed solely on mass production. The first is that measuring mass
production is only practical for small plants that can be easily harvested.
For larger plants, growth is more often measured as increment in either diameter
or height. For example, the CTFS monitors diameter growth in 49 large permanent
plots across forests worldwide \citep{Anderson-2015};
 forestry have likewise recorded growth in diameter across
large tracts of the globe \citep{Purves-2008}. The second problem is
that, as we outline further below, because mass production is only one
component of plant growth; theory focussing solely on mass production will
 always be limited.

@@

Ultimately, trait based understanding integrated wiht model of plant growth, also able to cpature patterns of growth through ontogeny. Growth rates tend to show hump-shaped relationship with size, when expressed as either height \citep{Sillett-2010, King-2011} or diameter growth \citep{Herault-2011}.  In contrast, basal-area growth continues to increase with size \citep{Sillett-2010, Stephenson-2014}, due to an increasing influence of stem turnover. All growth measures decrease sharply with size when expressed as relative growth rates \citep{Rees-2010, Iida-2014}. Shade tolerance tends to decrease with increasing size \citep{Lusk-2006}, due to increasing costs of mainatining stems \citep{Givnish-1988}

In this paper we provide a mechanistic framework for describing the potential
effect of traits on growth throughout a plant's life-cycle, linking to
commonly used metrics such as height and diameter growth. To help motivate our
study we re-analyse demographic and trait data from an earlier study
 \citep{Wright-2010}, to show 1) that the link between traits and
growth is stronger than previously thought, 2) that the influence of three
prominent traits on growth rate is moderated by plant size, and 3) that the
impact of size on the nature of relationships varies among traits
 \citep[see also]{Ruger-2012}. We then show how these results align with new
set of theoretical predictions. Analysis extends ...
Moreover, we show how traits moderate plant
responses to light environment and also determine shade tolerance, supporting
diverse empirical results \citep{Ruger-2012, Poorter-2006}. By
disentangling the effects of plant size, light environment and traits on
growth rates, we hope to provide a solid theoretical foundation for trait
ecology and thus provide a platform for understanding growth across diverse
species around the world.

@@

To make sense of empirical patterns, we extend a widely-used theoretical model that links growth rate in
seedlings to LMA \citep{Lambers-1992, Wright-2000}, to explicitly include influences of
size, light environment, and other prominent traits. This model

@@

We begin with a standard model for the amount of biomass available for
growth, ${\rm d}B / {\rm d}t$, given by the difference between income
(total photosynthesis) and losses (respiration and turnover) within the
plant \citep{Makela-1997, Thornley-2000, Falster-2011}:

@@

To model growth in either height, basal area or stem diameter requires that account not just for mass production, but also for the costs of building new tissues, allocation to reproduction, and architectural layout. Mathematically, height growth can be decomposed into a product of physiologically relevant terms \citep{Falster-2011}:

@@

The first term on the right of eq \ref{eq:dhdt},
${\rm d}H / {\rm d}A_{\rm l}$, is the growth in plant height
per unit growth in total leaf area -- accounting for the architectural
strategy of the plant. Some species tend to leaf out more than grow
tall, while other species emphasise vertical
extension \citep{Poorter-2006}.

@@

To address the first of these challenges, we use a functional balance
model \citep{Yokozawa-1995, Falster-2011} assuming
1) an allometric relation between total leaf area and plant height, and
2) a constant ratio between total leaf area and each of sapwood
cross-sectional area, bark cross-sectional area, and total root mass.
These assumptions, which are well-supported by data (Fig.
\ref{f-assumptions}), lead immediately to an allometric model for plant
size (Table \ref{tab:allometry}, see Supplementary material for
derivations). Substituting from Table \ref{tab:allometry} into eqs.
\ref{eq:dhdt}, \ref{eq:dast}, \ref{eq:dDdt} then gives an explicit model
for plant growth in relation to size.

@@

By definition, the main effect of increasing $\phi$ is to decrease the
marginal leaf deployment per mass (eq. \ref{eq:daldmt}) and thus reduce
growth rate. However, to fully account for the influence of $\phi$ on
growth we must also account for the decrease in leaf turnover that
results from superior leaf construction \citep{Wright-2004}.
This is achieved by linking the turnover rate of leaf in eq.
\ref{eq:dbdt} to $\phi$. We use an allometric scaling relationship of
the form $k_{\rm l}=\alpha_4 \, \phi^{-\beta_4}$, which has been
shown to describe patterns across diverse
ecosystems \citep{Wright-2004} (Fig. \ref{fS-leaf}).

As for leaf, cheaper stem construction (lower $\rho$) decreases the
cost of deploying a unit of leaf area, and may thereby increase growth
rates. However, the cost of cheap stem construction must also be
accounted for. However, the direct physiological trade-offs of lower
$\rho$ are less understood than for $\phi$. One possibility is that
lower $\rho$ decreases mechanical strength resulting in higher
mortality \citep{Chave-2009, Wright-2010}. Under
this scenario, decreasing $\rho$ will always provide a growth
advantage, because the costs of low $\rho$ are not realised within the
terms of eqs. \ref{eq:dhdt} and \ref{eq:dast} (Table
\ref{tab:trade-offs}). In addition, lower $\rho$ may increase turnover
of sapwood. Mirroring our assumptions for leaves, we let sapwood
turnover decrease with $\rho$,
i.e.$k_\textrm{ss}=\alpha_5 \, \rho^{-\beta_5}$, with $\beta_5 > 1$.

@@

This new growth model captures the intrinsically size-dependent nature
of plant growth, recovering well-known
empirical patterns \citep{Sillett-2010, King-2011}. Height growth shows a hump-shaped pattern
with size, first increasing then decreasing. This pattern results from
systematic changes in the four components of eq. \ref{eq:dhdt} with size
(Fig. \ref{f-conceptual}), including a strong decline in the fraction of plant
that is leaf declines with increasing size (Fig. \ref{f-mass_fraction}),
and increasing reproductive allocation. In contrast, basal-area growth
continues to increase with size \citep{Sillett-2010, Stephenson-2014},
due to an increasing influence of stem
turnover. Diameter growth shows a weakly hump shaped
curve \citep{Herault-2011}, tapering off slightly at larger
sizes, in part because of allometric effects (eq. \ref{eq:dDdt}, but
mainly because of increased reproductive allocation in older trees
(Fig?). All growth measures decrease sharply with size when expressed as
relative growth rates \citep{Iida-2014}.

@@

Two other important predictions arise directly from linking traits to
growth rate. First, traits moderate the
responsiveness of growth to changes in light environment. This response
arises simply because species with higher potential growth rate have
greater potential plasticity. Recent analyses have shown that species
with low $rho$ increase growth more substantially with incraeses in
light \citep{Ruger-2012}. This is exactly the behaviour
exhibited in our model (Fig. \ref{f-growth_light_dia}), at least for small
to intermediate sizes. At larger sizes (D=0.2m) however, the advantages
of low $\phi$ are lost (Fig. \ref{f-growth_light_dia}). This results also
agrees with empirical results showing that growth for species with low
$rho$ actually decreases as size
increases \citep{Ruger-2012}. In contrast, growth rate tends
to increase in size for the species with highest
$\rho$ \citep{Ruger-2012}.

Variation in $\phi$ also moderates the response of growth to changes
in light, with species having the lowest $rho$ being most responsive.
However, unlike for $\rho$, the effect appears only for the smallest
size classes. Accordingly, empirical analyses have detected such a link
in small plants but not for plants \textgreater{} 0.01m
dbh \citep{Ruger-2012}.

@@

Current theory emphasises the relationship between $\phi$ and the relative growth in plant mass
\citep{Lambers-1992, Cornelissen-1996, Wright-2000, Enquist-2007},
${\rm d}P / {\rm d}t / M_{\rm a}$. This relationship can be derived from eq. \ref{eq:dbdt}  by ...
(see Appendix \ref{app:traits-RGR}).

@@

@Osazuwa-2014 - indreases in WD through ontogeny.

@@

Second, species with low $\phi$ and low $\rho$ are predicted to be
less shade tolerant (Fig. \ref{f-wplcp}). At low $\phi$ ($\rho$),
leaf (sapwood) turnover is higher and thus a greater light income is
needed to offset these costs. As previously suggested
 \citep{Givnish-1988}, shade-tolerance also decreases with
height because as size increase, the total amount of energy needed to
offset respiratory and turnover costs in the stem also increases. These
finding matches well known empirical patterns, where both $\phi$ and
$\rho$ have been linked to shade tolerance \citep{Poorter-2006, Lusk-2008,osunkoya-1996}.

@@

Although Eq. \ref{eq:RGR} captures patterns of growth in seedlings in
relation to $\phi$\citep{Wright-2000}, this
approximation does not directly link to other traits, or to the
variables that are routinely collected for large trees: namely plant
height ($h$) and stem cross-sectional area ($A_{\rm st}$) or
diameter $D$.

@@

Note, scaling relationship reversed from \citep{Falster-2011}.

@@

We follow the model of \citep{Yokozawa-1995} describing the
vertical distribution of leaf area within the crowns of individual
plants. This model can account for a variety of canopy profiles through
a single parameter $\eta$. Setting $\eta=1$ results in a conical
canopy, as seen in many conifers, while higher values, e.g. $\eta=12$
, give a top-weighted canopy profile similar to those seen among
angiosperms. Let $S(z,h)$ be the sapwood area at height $z$ for a
plant with top height $h$. Following Yokozawa and Hara (1995) we
assume a relationship between $S(z,h)$ and height such that

@@

We also assume that each unit of sapwood area supports a fixed area of
leaf (the pipe model, \citep{Shinozaki-1964}), so that the total
canopy area of a plant relates to basal sapwood area $S(0,h)$:

@@

where
$\eta_c=1-\frac{2}{1+\eta} + \frac{1}{1+2\eta}$ \citep{Yokozawa-1995}.
Substituting from eq. \ref{eq:crown2} into eq. \ref{eq:ms1} gives an
expression for sapwood mass as a function leaf area and height:

@@

\begin{figure}[ht]
\centering
\includegraphics{SI/lmA_tradeoff.pdf}
\caption{\textbf{Leaf turnover decreases with leaf-construction cost.}
Data from \citep{Wright-2004} for 678 species from 51 sites, each
point giving a species-average. Lines show standardised major axis lines
fitted to data from each site, with intensity of shading adjusted
according to strength of the relationship.\label{fS-leaf}}
\end{figure}
